Secure Composition of SPECTRE Mitigations

### 2023-11-03 prisc-spectre/prisc.tex
.

It remains to show \Thmref{def:compat}.
Without a proof of \Thmref{def:compat}, the composition of mitigations may not provide the security guarantees of interest, since one could intuitively ,,undo'' what another one did.
For space reasons, this extended abstract does not provide formal proof for all possible compositions of above mitigations, but at least sketches the anticipated proofs of compatibility theorems in \Cref{fig:rels}.

>>>>

It remains to show \Thmref{def:compat}.
Without a proof of \Thmref{def:compat}, the composition of mitigations may not provide the security guarantees of interest, since one could intuitively ,,undo'' what another one did.
This extended abstract does not provide formal proof for all possible compositions of above mitigations, but sketches the anticipated proofs of compatibility theorems in \Cref{fig:rels}.
